% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

% \cvtag{Hard-working (18/24)}
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

% \cvtag{UX}
% \cvtag{Mobile Devices \& Applications}
% \cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}


\cvsection{Experience}
% TODO: uncomment this to add new position
% \cvexperience{Software Engineer Intern}{May 2021 -- Present}{Pittsburgh, PA}{NetApp}
% \begin{itemize}
%     \item Place-Holder
%     \item Place-Holder
% \end{itemize}
\cvexperience{Software Engineer Intern}{May 2021 -- August 2021}{Pittsburgh, PA}{NetApp Inc.}
\begin{itemize}
    \item Implemented REST API content management approaches in Python.
    \item Engaged in code reviews and discussions with industry professionals to
          ensure quality of contributions.
    \item Participated in Agile and Scrum meetings to manage and track tasks.
\end{itemize}
\cvexperience{Techinal Leader}{Aug. 2020 -- May 2022}{Meadville, PA}{Computer Science Department, Allegheny College}
\begin{itemize}
    \item Assisted 10-15  student weekly in successfully completing class
          activities and \\ assignments
    \item Held weekly office hours to assist and support student's academic
          progress in introductory and intermediate computer science courses
    \item Attended meetings to receive performance feedback and provide updates
\end{itemize}
\cvexperience{Capstone Project Intern}{Jan. 2021 -- May 2021}{Meadville, PA}{NetApp, Allegheny College}
\begin{itemize}
    \item Collaborated in an Agile environment and attended weekly sprint meetings
    \item Utilized React Javascript framework to implement new functionalities
          and \\ enhance existing ones
    \item Presented findings and results to a team of 35-40 software engineers
\end{itemize}
\cvexperience{Teacher Assistant}{Feb. 2021 -- May 2021}{Meadville, PA}{World Languages Department, Allegheny College}
\begin{itemize}
    \item Assisted 20 students in beginner and intermediate Arabic during 4 weekly
          labs, tailoring teaching approaches to that of student’s learning style
    \item Prepared and construct lesson plans according to professors requirements and current topics
    \item Created a fun, inclusive, and productive environment for students seeking to learn the Arabic language
\end{itemize}
% \cvexperience{Office Intern}{Aug. 2019 -- Mar. 2020 }{Meadville, PA}{Financial Aid Office, Allegheny College}
% \begin{itemize}
%     \item Answered phone calls and assisted callers according to their concern regarding financial aid
%     \item Made appointments for supervisors and organized their schedules
%     \item Sorted and filed sensitive office documents and records in alphabetical order
% \end{itemize}
\cvsection{Projects}
\cvproject{AFLuent \href{https://github.com/AFLuent/AFLuent}{\githubsymbol}}{May 2022}{}
% TODO: AFLUENT
\begin{itemize}
    \item Automated Fault Localization tool in Python integrated directly into
          Pytest testing framework
    \item Submitted a
          \underline{\textbf{\href{https://noorbuchi.netlify.app/thesis/thesis.pdf}{senior
                      thesis}}} to showcase its features and evaluation
\end{itemize}
\cvproject{Ethereum Dice Game \href{https://allegheny-computerscience-302-s2022.github.io/cmpsc-302-project-antlet-noorbuchi/}{\homepagesymbol}}{May 2022}{}
\begin{itemize}
    \item Game logic and Ethereum contract implemented in Solidity
\end{itemize}
\cvproject{SheetShuttle \href{https://github.com/GatorEducator/SheetShuttle}{\githubsymbol}}{April 2022}{}
\begin{itemize}
    \item Utilizes Google Sheets and GitHub's APIs to transfer information using
          customizable plugins.
\end{itemize}
\cvproject{PyGo Stock Portfolio Tracker
    \href{https://github.com/noorbuchi/PyGo-Portfolio-Tracker}{\githubsymbol}}{Dec.
    2020}{}
\begin{itemize}
    \item Computation and data storage using Go programming language
    \item Front-end web application using Python's Streamlit
    \item Retrieves real-time stock market through Google Finance
\end{itemize}
\cvproject{2-3 B-Tree Visualizer \href{https://github.com/noorbuchi/2-3-B-Tree-Java}{\githubsymbol}}{May 2020}{}
\begin{itemize}
    \item Built using Java and Graphviz to visualize 2-3 B-Trees
    \item Implementation of insertion, deletion, and breadth-first traversal
\end{itemize}
\cvproject{Cogitate \href{https://github.com/GatorCogitate/cogitate_tool}{\githubsymbol}}{Mar. 2020}{}
\begin{itemize}
    \item Built using Python to retrieve and analyze statistics from GitHub repositories
    \item Display data through Streamlit web application
\end{itemize}
\cvproject{GatorSorter Sorting
    \href{https://github.com/Allegheny-Computer-Science-101-F2019/Gator-Sorter}
    {\githubsymbol}}{Nov. 2019}{}
\begin{itemize}
    \item Implementation of basic sorting algorithms in Java with Step by step demonstration of Bubble Sort, Insertion Sort, and Selection Sort
\end{itemize}

% \cvsection{Leadership}
% \cvexperience{Club President}{Feb. 2021--Present}{Meadville, PA}{Chess Club at Allegheny College}
% \begin{itemize}
%     \item Organize club events and activities for 10-14 members
%     \item Coordinate general and executive board meetings
%     \item Keep track of club budget and expenses
% \end{itemize}


%% \cvsection{PUBLICATIONS}
%% \smallskip
%% \begin{itemize}
%% \item R. Jain, H. Tulsani, A. Bansal, "A two- tier steganographic model based on (2,2)VCS %% and integer wavelet transform", in Preceding of The 5th International Conference on %% Computing for Sustainable Global Development organized by IEEE, pp. 4731-4734, (2018).
%%\smallskip
%%\end{itemize}
